---
title: "Seattle_Pets"
author: "Lamar Foster"
date: "5/6/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

theme_set(theme_light())
```

```{r}
library(tidyverse)
library(lubridate)
```

```{r}
seattle_pets <-read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-03-26/seattle_pets.csv") %>% 
    mutate(license_issue_date = mdy(license_issue_date)) 
```


```{r}
head(seattle_pets)

seattle_pets %>% 
  count(animals_name, sort = T)
```

```{r}
seattle_pets %>% 
  mutate(license_issue_date = mdy(license_issue_date)) %>% 
  count(year = year(license_issue_date))

seattle_pets %>% 
  count(species, primary_breed, sort = T) %>% 
  filter(species %in% c("Cat", "Dog")) %>% 
  mutate(percent = n / sum(n)) %>% 
  group_by(species) %>% 
  top_n(10, percent) %>% 
  #ungroup() %>% 
  mutate(primary_breed = fct_reorder(primary_breed, percent)) %>% 
  ggplot(aes(primary_breed, percent, fill = species)) +
  geom_col(show.legend = F) +
  scale_y_continuous(labels = scales::percent) + 
  facet_wrap(~species, ncol = 1, scales = "free_y") +
  coord_flip() +
  labs(x = "Primary Breed", y = "Percent", title= "Most common cat and dog breeds", subtitle = "licensed pets in Seatlle")

```

```{r}
dogs <- seattle_pets %>% 
  filter(species == "Dog")

name_breed_count <- dogs %>% 
  group_by(animals_name) %>% 
  add_count(animals_name) %>% 
  mutate(name_total = n()) %>% 
  group_by(primary_breed) %>% 
  mutate(breed_total = n()) %>% 
  count(animals_name, primary_breed, name_total, breed_total) 


name_breed_count %>% 
  filter(name_total >= 200, 
         breed_total >= 200) %>% 
  mutate(percent_of_breed = n / breed_total, 
         percent_overall = name_total / nrow(dogs)) %>% 
  mutate(overrepresented_ratio = percent_of_breed / percent_overall) %>% 
  arrange(desc(overrepresented_ratio))
```

Hypergeometric Tests - In probability theory and statistics, the hypergeometric distribution is a discrete probability distribution that describes the probability of {\displaystyle k}k successes (random draws for which the object drawn has a specified feature) in {\displaystyle n}n draws, without replacement, from a finite population of size {\displaystyle N}N that contains exactly {\displaystyle K}K objects with that feature, wherein each draw is either a success or a failure.








